Figure 2 - Overview heatmaps for IP-MS and ChIP

### 2024-07-15 ms_figure_2_overview-heatmaps.Rmd
Make IP-MS heatmaps wider (Fig 2), adjust legends and titles

## Heatmap sizes
w_ipmsHm <-  84 # heatmap body width (mm)
h_ipmsHm <- 178 # total heatmap height (mm)
w_peaksHm <-  84 # heatmap body width (mm)
h_peaksHm <- 178 # total heatmap height (mm)

@@

hm1a <- Heatmap(hmdata_150$tstat, 
                cluster_rows = FALSE, 
                cluster_columns = FALSE, 
                col = makeHeatmapCol(hmdata_150$tstat, stringency = "high"), 
                border = TRUE, 
                border_gp = gpar(lwd = 0.5),
                column_split = hmdata_150$colsplit, 
                name = "Mod.\nt-stat.", 
                na_col = binary_heatmap_colors["FALSE"],
                column_names_gp = gpar(fontsize = fs),
                row_names_gp = gpar(fontsize = fs),
                row_title = "Proteins significantly enriched in at least one experiment",
                row_title_gp = gpar(fontsize = fl),
                show_row_names = FALSE, show_column_names = FALSE,
                use_raster = FALSE, show_heatmap_legend = TRUE,
                right_annotation = makeComplexAnnotation(
                    hmdata_150$tstat, complexes[complexLabel], 
                    idmap = idmap),
                bottom_annotation = makeColLabels(hmdata_150$tstat, colLabel_150, fl),
                width = unit(w_ipmsHm, "mm"), # heatmap body width
                heatmap_height = unit(h_ipmsHm, "mm"), # whole heatmap height
                column_title_gp = gpar(fontsize = ft),
                heatmap_legend_param = list(title_gp = gpar(fontsize = fl), 
                                border = "gray10",
                                border_gp = gpar(lwd = 0.5)))

set.seed(42L)
hm_150 <- grid.grabExpr(
    hm1a <- draw(hm1a, merge_legend = TRUE,
                heatmap_legend_side = "right",
                annotation_legend_side = "right"),
    width = w_ipmsHm, height = h_ipmsHm
)

@@

hm2a <- Heatmap(hmdata_500$tstat, 
                cluster_rows = FALSE, 
                cluster_columns = FALSE, 
                col = makeHeatmapCol(hmdata_500$tstat, stringency = "high"), 
                border = TRUE, 
                border_gp = gpar(lwd = 0.5),
                column_split = hmdata_500$colsplit, 
                name = "Mod.\nt-stat.", 
                na_col = binary_heatmap_colors["FALSE"],
                column_names_gp = gpar(fontsize = fs),
                row_names_gp = gpar(fontsize = fs),
                row_title = "Proteins significantly enriched in at least one experiment",
                row_title_gp = gpar(fontsize = fl),
                show_row_names = FALSE, show_column_names = FALSE,
                use_raster = FALSE, show_heatmap_legend = TRUE,
                right_annotation = makeComplexAnnotation(hmdata_500$tstat, complexes[complexLabel],
                                                         idmap = idmap, show_legend = FALSE),
                bottom_annotation = makeColLabels(hmdata_500$tstat, colLabel_500, fl),
                width = unit(w_ipmsHm, "mm"), # heatmap body width
                heatmap_height = unit(h_ipmsHm, "mm"), # whole heatmap height
                column_title_gp = gpar(fontsize = ft),
                heatmap_legend_param = list(title_gp = gpar(fontsize = fl), 
                                border = "gray10",
                                border_gp = gpar(lwd = 0.5)))

hm_500 <- grid.grabExpr(
    hm2a <- draw(hm2a, merge_legend = TRUE,
                 heatmap_legend_side = "right",
                 annotation_legend_side = "right"),
    width = w_ipmsHm, height = h_ipmsHm
)

>>>>

## Heatmap sizes
w_ipmsHm <-  1.2 * 84 # heatmap body width (mm)
h_ipmsHm <- 178 # total heatmap height (mm)
w_peaksHm <-  84 # heatmap body width (mm)
h_peaksHm <- 178 # total heatmap height (mm)

@@

hm1a <- Heatmap(hmdata_150$tstat, 
                cluster_rows = FALSE, 
                cluster_columns = FALSE, 
                col = makeHeatmapCol(hmdata_150$tstat, stringency = "high"), 
                border = TRUE, 
                border_gp = gpar(lwd = 0.5),
                column_split = hmdata_150$colsplit, 
                name = "Mod. t-stat.", 
                na_col = binary_heatmap_colors["FALSE"],
                column_names_gp = gpar(fontsize = fs),
                row_names_gp = gpar(fontsize = fs),
                row_title = "Proteins significantly enriched in at least one experiment",
                row_title_gp = gpar(fontsize = fl),
                show_row_names = FALSE, show_column_names = FALSE,
                use_raster = FALSE, show_heatmap_legend = TRUE,
                right_annotation = makeComplexAnnotation(
                    hmdata_150$tstat, complexes[complexLabel], 
                    idmap = idmap),
                bottom_annotation = makeColLabels(hmdata_150$tstat, colLabel_150, fl),
                width = unit(w_ipmsHm, "mm"), # heatmap body width
                heatmap_height = unit(h_ipmsHm, "mm"), # whole heatmap height
                column_title_gp = gpar(fontsize = ft),
                heatmap_legend_param = list(title_gp = gpar(fontsize = fl), 
                                            legend_direction = "horizontal",
                                            title_position = "topcenter",
                                            border = "gray10",
                                            border_gp = gpar(lwd = 0.5)))

set.seed(42L)
hm_150 <- grid.grabExpr(
    hm1a <- draw(hm1a, merge_legend = TRUE,
                heatmap_legend_side = "bottom",
                annotation_legend_side = "bottom"),
    width = w_ipmsHm, height = h_ipmsHm
)

@@

hm2a <- Heatmap(hmdata_500$tstat, 
                cluster_rows = FALSE, 
                cluster_columns = FALSE, 
                col = makeHeatmapCol(hmdata_500$tstat, stringency = "high"), 
                border = TRUE, 
                border_gp = gpar(lwd = 0.5),
                column_split = hmdata_500$colsplit, 
                name = "Mod. t-stat.", 
                na_col = binary_heatmap_colors["FALSE"],
                column_names_gp = gpar(fontsize = fs),
                row_names_gp = gpar(fontsize = fs),
                row_title = "Proteins significantly enriched in at least one experiment",
                row_title_gp = gpar(fontsize = fl),
                show_row_names = FALSE, show_column_names = FALSE,
                use_raster = FALSE, show_heatmap_legend = TRUE,
                right_annotation = makeComplexAnnotation(hmdata_500$tstat, complexes[complexLabel],
                                                         idmap = idmap, show_legend = FALSE),
                bottom_annotation = makeColLabels(hmdata_500$tstat, colLabel_500, fl),
                width = unit(w_ipmsHm, "mm"), # heatmap body width
                heatmap_height = unit(h_ipmsHm, "mm"), # whole heatmap height
                column_title_gp = gpar(fontsize = ft),
                heatmap_legend_param = list(title_gp = gpar(fontsize = fl), 
                                            legend_direction = "horizontal",
                                            title_position = "topcenter",
                                            border = "gray10",
                                            border_gp = gpar(lwd = 0.5)))

hm_500 <- grid.grabExpr(
    hm2a <- draw(hm2a, merge_legend = TRUE,
                 heatmap_legend_side = "bottom",
                 annotation_legend_side = "bottom"),
    width = w_ipmsHm, height = h_ipmsHm
)
